---
title: "Viridis Color Palettes"
author: "Your name"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include = FALSE}
# Set global knit options (optional)
knitr::opts_chunk$set(echo = FALSE)

# load packages
library(tidyverse)
library(viridis)
library(here)
library(maps)
library(sf)

# load data and functions
source(here("R/plot_temps.R"))
```

<!--Each second level header begins a new slide-->
## Viridis

The [viridis](https://sjmgarnier.github.io/viridis/) package provides eight eye-catching color palettes to use in data visualizations:

- magma
- inferno
- plasma
- viridis
- cividis
- rocket
- mako
- turbo

## Optimized for perception

According to the virids documentation, the palettes:

> are designed to improve graph readability for readers with common forms of color blindness and/or color vision deficiency. The color maps are also perceptually-uniform, both in regular form and also when converted to black-and-white for printing.

## Magma

```{r magmas}
plot_temps("magma", title = FALSE)
```


## Inferno

```{r inferno}
plot_temps("inferno", title = FALSE)
```

## Plasma

```{r plasma}
plot_temps("plasma", title = FALSE)
```

## Viridis

```{r viridis}
plot_temps("viridis", title = FALSE)
```

## Cividis

```{r cividis}
plot_temps("cividis", title = FALSE)
```

## Rocket

```{r rocket}
plot_temps("rocket", title = FALSE)
```

## Mako

```{r mako}
plot_temps("mako", title = FALSE)
```

## Turbo

```{r turbo}
plot_temps("turbo", title = FALSE)
```

## Usage

To use a viridis palette in your plot, include `scale_*_viridis()` in your ggplot2 call:

```{r eval = FALSE, echo = TRUE}
mpg |>  
  ggplot(aes(x = displ, y = cty, color = hwy)) +
    geom_point() +
    scale_color_viridis(option = "A")
```

