---
title: "Viridis Color Palettes"
author: "Your name"
date: "`r Sys.Date()`"
runtime: shiny
---

<!--This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).-->

```{r setup, include = FALSE}
# Set global knit options (optional)
knitr::opts_chunk$set(echo = FALSE)

# load_packages
library(shiny)
library(tidyverse)
library(viridis)
library(here)
library(maps)
library(sf)

# load data and functions
source(here("R/plot_temps.R"))
```

## Viridis

The [viridis](https://sjmgarnier.github.io/viridis/) package provides eight eye-catching color palettes to use in data visualizations:

- magma
- inferno
- plasma
- viridis
- cividis
- rocket
- mako
- turbo

## Optimized for perception

According to the virids documentation, the palettes:

> are designed to improve graph readability for readers with common forms of color blindness and/or color vision deficiency. The color maps are also perceptually-uniform, both in regular form and also when converted to black-and-white for printing.

## Viridis in action

Each plot uses a different viridis color palette to visualize the median high temperature (F) by US county.

```{r palettes, echo=FALSE}
inputPanel(
  selectInput(
    "palette", 
    label = "Select a palette",
    choices = c("magma",
                "inferno",
                "plasma", 
                "viridis", 
                "cividis", 
                "rocket", 
                "mako", 
                "turbo"), 
    selected = "magma"
  )
)

renderPlot({
  plot_temps(input$palette)
})
```

## Usage

To use a viridis palette in your plot, include `scale_*_viridis()` in your ggplot2 call:

```{r eval = FALSE, echo = TRUE}
mpg |>  
  ggplot(aes(x = displ, y = cty, color = hwy)) +
    geom_point() +
    scale_color_viridis(option = "A")
```

